Short Report on Mass Spectrometry

### 2024-10-27 dev/dev_template_dashboard.qmd

---
title: "Short Dashboard for Mass Spectrometry"
logo: C:/Users/cunha/Documents/007_CodeProjects/StreamFindData/inst/extdata/logo_StreamFind.png
format:
  dashboard:
    theme: lux
    self-contained: true
    embed-resources: true
    nav-buttons:
      - icon: github
        href: https://github.com/odea-project/StreamFind
editor_options:
  chunk_output_type: console
---

@@

options(DT.options = list(
  bPaginate = TRUE, 
  dom = "lfrtip",
  pageLength = 20,
  lengthMenu =c(10, 15, 20, 25, 50, 75, 100),
  language = list(info = 'Showing page _PAGE_ of _PAGES_')
))
```

>>>>

---
title: "Short Dashboard for Mass Spectrometry"
logo: "`r file.path(system.file(package = 'StreamFind', dir = 'extdata'), 'logo_StreamFind.png')`"
format:
  dashboard:
    theme: lux
    self-contained: true
    embed-resources: true
    nav-buttons:
      - icon: github
        href: https://github.com/odea-project/StreamFind
editor_options:
  chunk_output_type: console
---

@@

options(DT.options = list(
  bPaginate = TRUE, 
  dom = "lfrtip",
  pageLength = 20,
  lengthMenu = c(10, 15, 20, 25, 50, 75, 100),
  language = list(info = 'Showing page _PAGE_ of _PAGES_')
))
```

### 2024-10-27 dev/dev_template_report.qmd
linked Rhdf5lib and test function

```{r}
#| include: false
options(DT.options = list(
  dom = "lfrtip",
  autoWidth = TRUE,
  pageLength = 10,
  lengthMenu = c(10, 20, 50, 75, 100),
  initComplete = htmlwidgets::JS(
    "function(settings, json) {",
    "$(this.api().table().body()).css({'font-size': '12px'});",
    "$(this.api().table().body()).css({'white-space': 'nowrap'});",
    "}"
  )
))
```

```{r}
#| include: false
library(knitr)
library(kableExtra)
library(data.table)
library(DT)
library(magrittr)
library(ggplot2)
library(plotly)
library(StreamFind)
```

```{r}
#| include: false
ms_files <- StreamFindData::get_ms_file_paths()[10:27]
db <- StreamFindData::get_ms_tof_spiked_chemicals_with_ms2()
cols <- c("name", "formula", "mass", "rt", "fragments", "tag")
db <- db[, cols, with = FALSE]
dbis <- db[grepl("IS", db$tag), ]
dbsus <- db[!grepl("IS", db$tag), ]
path <- "C:/Users/apoli/Documents/example_ms_files"
```

>>>>

```{r}
#| include: false

options(DT.options = list(
  dom = "lfrtip",
  autoWidth = TRUE,
  pageLength = 10,
  lengthMenu = c(10, 20, 50, 75, 100),
  initComplete = htmlwidgets::JS(
    "function(settings, json) {",
    "$(this.api().table().body()).css({'font-size': '12px'});",
    "$(this.api().table().body()).css({'white-space': 'nowrap'});",
    "}"
  )
))
```

```{r}
#| include: false

library(knitr)
library(kableExtra)
library(data.table)
library(DT)
library(magrittr)
library(ggplot2)
library(plotly)
library(StreamFind)
```

```{r}
#| include: false

ms_files <- StreamFindData::get_ms_file_paths()[10:27]
db <- StreamFindData::get_ms_tof_spiked_chemicals_with_ms2()
cols <- c("name", "formula", "mass", "rt", "fragments", "tag")
db <- db[, cols, with = FALSE]
dbis <- db[grepl("IS", db$tag), ]
dbsus <- db[!grepl("IS", db$tag), ]
path <- "C:/Users/apoli/Documents/example_ms_files"
```
